---
title: "Lab 7 - Multiple Linear Regression"
author: "Chase Tarr"
date: "11/8/2021"
output: html_document
---

```{r setup, include=TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach the packages we need

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Intro to ggpairs
 - Use GGally::ggpairs() function to create a pairs plot
```{r}
ggpairs(penguins)
```
 
```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% # selecting columns
  ggpairs(aes(color = species))

ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) +
  geom_point(aes(color = species)) + # critical to use the right variable included or excluded
  geom_smooth(method = "lm")
```

## Multiple Linear Regression - Penguins
 - Use multiple linear regression to try to understand the relationship between multiple predictor variables and a single continuous outcome variable (body mass).

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# return just the coefficients:
penguin_lm
```

How would you interpret this coefficient for flipper_length_mm?
 - On average, we would expect a 51.54 gram increase in penguin body mass for every 1mm increase in flipper length if everything else is held constant. **USE IN LINE CODE REFERENCING**
 
 Use `summary()` function to get more information
```{r}
summary(penguin_lm)
```
What does this R-squared value of 0.7596 mean for this model?
 - The R-squared value of 0.7596 means there is 76% of variance in penguin body mass is explained by this model **there is no good or bad R-squared value**
 
### Using the `broom` functions tidy and glance

Use broom::tidy to get the coefficient summary in a data frame.
Use broom::glance to get the data summary in a data frame.
```{r}
penguin_lm_tidy <- tidy(penguin_lm)
penguin_lm_tidy
```

Try using in-line code to refer to (print) the bill depth coefficient
  `r penguin_lm_tidy$estimate[3]`
  
```{r}
penguin_lm_glance <- glance(penguin_lm)

penguin_lm_glance
```

## Try another model
 - We have thought really hard, done a literature review, consulted with experts, deeply explored our data, and decided that the three most critical variables to include in this model are:
    - flipper length
    - species
    - sex
    
Task: create a multiple linear regression model using 3 predictor variables
then, take a look a the model outputs and interpret the coefficients with a neighbor

```{r}
penguin_lm_task <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

penguin_lm_task
```
 - reference level for species is Adelie, reference level for sex is female
 
 mass(g) = -365.82 + 20.02(flipper length mm) - 87.63(Chinstrap) + 836.26(Gentoo) + 530.38(Male)
 
 if everything else is held constant, we expect on average a Gentoo penguin to be 836.26 grams larger than an Adelie penguin
 
 if everthing else is held constant, on average we expect a male penguin to weight 530.4 grams more than a female
  
  
## Use broom::augment() to see predicted values

```{r}
augment(penguin_lm_task)
```

## Use plot() to look at model diagnostics

```{r}
plot(penguin_lm_task) # looking at cooks distance will illustrate outliers in data
```

 - Conceptual understanding and expertise allows me to responsibly determine that penguin species, sex, and flipper length are reasonable predictor variable (make sure you're thinking hard about variables adn different variable combinations)
 - Diagnostic plots all check out for normality of residuals, homosedasticity, and no worrisome outliers (<< last one not an assumption)

## Make output tables
 - Using modelsummary:
```{r}
modelsummary(penguin_lm_task)
```

Using stargazer:
```{r, results = "asis"}
stargazer(penguin_lm_task, type = "html")
```


